Web Service Community \\ Learning

### 2014-07-06 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

>>>>

In the presence of multiple service candidates with identical or similar functionalities, quality of service (QoS) provides nonfunctional characteristics for the optimal candidate selection. Based on the previous investigations [2, 10, 14], we identify the most representative QoS properties of Web services in the following
